---
title: "Using UCI Adult Dataset for Logistic regression"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    keep_md: yes
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data


```{r load-data}
adult <- read.csv('adult_sal.csv')
head(adult)
adult <- select(adult,-X)
head(adult)
```

```{r}
str(adult)
summary(adult)
```


* * *

## Part 1:Research question
We will be attempting to predict if people in the data set belong in a certain class by salary, either making <=50k or >50k per year.

* * *


## Part 2: Data Cleaning

We have a lot of columns that are cateogrical factors, however a lot of these columns have too many factors than may be necessary.




```{r}
table(adult$type_employer)
```
Combining Never-worked and Without-pay into a single group called "Unemployed"

```{r}
unemp <- function(job){
    job <- as.character(job)
    if (job=='Never-worked' | job=='Without-pay'){
        return('Unemployed')
    }else{
        return(job)
    }
}
```


```{r}
adult$type_employer <- sapply(adult$type_employer,unemp)
```

```{r}
table(adult$type_employer)
```

Combining State and Local gov jobs into a category called SL-gov and combining self-employed jobs into a category called self-emp.


```{r}
group_emp <- function(job){
    if (job=='Local-gov' | job=='State-gov'){
        return('SL-gov')
    }else if (job=='Self-emp-inc' | job=='Self-emp-not-inc'){
        return('self-emp')
    }else{
        return(job)
    }
}
```



```{r}
adult$type_employer <- sapply(adult$type_employer,group_emp)
```


```{r}
table(adult$type_employer)
```


```{r}
table(adult$marital)
```
Reducing this to three groups:
Married
Not-Married
Never-Married

```{r}
group_marital <- function(mar){
    mar <- as.character(mar)
    
    # Not-Married
    if (mar=='Separated' | mar=='Divorced' | mar=='Widowed'){
        return('Not-Married')
    
    # Never-Married   
    }else if(mar=='Never-married'){
        return(mar)
    
     #Married
    }else{
        return('Married')
    }
}
```

```{r}

adult$marital <- sapply(adult$marital,group_marital)
table(adult$marital)
```


```{r}

table(adult$country)
```

```{r}
levels(adult$country)
```

```{r}
Asia <- c('China','Hong','India','Iran','Cambodia','Japan', 'Laos' ,
          'Philippines' ,'Vietnam' ,'Taiwan', 'Thailand')

North.America <- c('Canada','United-States','Puerto-Rico' )

Europe <- c('England' ,'France', 'Germany' ,'Greece','Holand-Netherlands','Hungary',
            'Ireland','Italy','Poland','Portugal','Scotland','Yugoslavia')

Latin.and.South.America <- c('Columbia','Cuba','Dominican-Republic','Ecuador',
                             'El-Salvador','Guatemala','Haiti','Honduras',
                             'Mexico','Nicaragua','Outlying-US(Guam-USVI-etc)','Peru',
                            'Jamaica','Trinadad&Tobago')
Other <- c('South')
```

```{r}
group_country <- function(ctry){
    if (ctry %in% Asia){
        return('Asia')
    }else if (ctry %in% North.America){
        return('North.America')
    }else if (ctry %in% Europe){
        return('Europe')
    }else if (ctry %in% Latin.and.South.America){
        return('Latin.and.South.America')
    }else{
        return('Other')      
    }
}
```

```{r}
adult$country <- sapply(adult$country,group_country)
```

```{r}

table(adult$country)
```

```{r}

str(adult)
```

```{r}

adult$type_employer <- sapply(adult$type_employer,factor)
adult$country <- sapply(adult$country,factor)
adult$marital <- sapply(adult$marital,factor)
```

```{r}

str(adult)
```

## Part 3: Missing Data
Converting any cell with a '?' or a ' ?' value to a NA value

```{r}
adult[adult == '?'] <- NA
```

```{r}

table(adult$type_employer)
```

```{r}
adult$type_employer <- sapply(adult$type_employer,factor)
adult$country <- sapply(adult$country,factor)
adult$marital <- sapply(adult$marital,factor)
adult$occupation <- sapply(adult$occupation,factor)
```

```{r}
library(Amelia)
missmap(adult)
```

```{r}

missmap(adult,y.at=c(1),y.labels = c(''),col=c('yellow','black'))
```
Omitting The missing Data as finding average or other subtitutes is not possible.

```{r}
adult <- na.omit(adult)
```

```{r}
missmap(adult,y.at=c(1),y.labels = c(''),col=c('yellow','black'))
```

* * *

## Part 4:EDA

```{r}
str(adult)
```

```{r}
ggplot(adult,aes(age)) + geom_histogram(aes(fill=income),color='black',binwidth=1) + theme_bw()
```

```{r}
ggplot(adult,aes(hr_per_week)) + geom_histogram() + theme_bw()
```

```{r}

#Lots of ways to do this, could use dplyr as well
names(adult)[names(adult)=="country"] <- "region"

```

```{r}
str(adult)
```

Creating a barplot of region with the fill color defined by income class

## Part 5:Mdeling

splitting data into test and train.
```{r}
library(caTools)

set.seed(101) 


sample <- sample.split(adult$income, SplitRatio = 0.70) 

# Training Data
train = subset(adult, sample == TRUE)

# Testing Data
test = subset(adult, sample == FALSE)
```

Training the model

```{r}
model = glm(income ~ ., family = binomial(logit), data = train)
```



```{r}
summary(model)
```



```{r}
new.step.model <- step(model)
```

 

```{r}
summary(new.step.model)
```

Creating a confusion matrix

```{r}
test$predicted.income = predict(model, newdata=test, type="response")

table(test$income, test$predicted.income > 0.5)
```
Accuracy

```{r}
(6372+1423)/(6372+1423+548+872)
```

```{r}

#recall
6732/(6372+548)
```


```{r}

#precision
6732/(6372+872)
```



